### 2012-01-27 docs/visualization/visualization.tex
add sample output
more plotsinglevar documentation

\section{Plotfiles}

@@

\section{Visualizing with \amrvis}

\section{Visualizing with \visit}

\section{Visualizing with {\tt data\_processing} scripts}

{\tt data\_processing/python\_plotfile} provide a simple commandline tool for doing 
visualizations of 2-d BoxLib plotfiles.  The main driver
is written in python and uses a set of Fortran routines, compiled with
{\tt f2py} to interface with the plotfile data.  To use the routine,
you will need to have {\tt matplotlib} and {\tt f2py} installed.  On
a machine running Fedora linux, you can install these packages via
\begin{verbatim}
yum install python-matplotlib f2py
\end{verbatim}

The library required by the python routines can be built by typing
'{\tt make}' in that directory.  If successful, you should find
a library {\tt fsnapshot.so}.  A simple plot can be made via:
\begin{verbatim}
plotsinglevar.py --log -o test.png plt00000/ tfromp
\end{verbatim}
This will make a plot of ``tfromp'' from the plotfile {\tt plt00000} with log scaling,
and store the output in {\tt test.png}.
If you don't do `{\tt -o}', then a default output filename consisting of the
plotfile name + component will be used.

\section{Visualizing with \yt}
\yt is a Python package for analyzing and visualizing simulation data.
Originally \yt was written for the {\tt Enzo} code, with focus on
cosmological simulation data.  It has since been refactored to remove
the specific {\tt Enzo}isms, and now can work on various data formats,
such as the BoxLib data from \maestro\ and \castro, HDF5 data
from {\tt FLASH}, and data from the SPH code {\tt Gadget}.  For more
information, see the \yt homepage at {\tt http://yt.enzotools.org/}.

>>>>

%-----------------------------------------------------------------------------
% plotfiles
%-----------------------------------------------------------------------------
\section{Plotfiles}

@@

%-----------------------------------------------------------------------------
% amrvis
%-----------------------------------------------------------------------------
\section{Visualizing with \amrvis}

%-----------------------------------------------------------------------------
% VisIt
%-----------------------------------------------------------------------------
\section{Visualizing with \visit}

%-----------------------------------------------------------------------------
% data_procesing
%-----------------------------------------------------------------------------
\section{Visualizing with {\tt data\_processing} scripts}

{\tt data\_processing/python\_plotfile} provide a simple commandline
tool for doing visualizations of 2-d \boxlib\ plotfiles, and slices
through 3-d \boxlib\ plotfiles.  The main driver is written in python
and uses a set of Fortran routines, compiled with {\tt f2py} to
interface with the plotfile data.  To use the routine, you will need
to have {\tt matplotlib} and {\tt f2py} installed.  On a machine
running Fedora linux, you can install these packages via
\begin{verbatim}
yum install python-matplotlib f2py
\end{verbatim}

The library required by the python routines can be built by typing
'{\tt make}' in that directory.  If successful, you should find
a library {\tt fsnapshot.so}.  A simple plot can be made via:
\begin{verbatim}
plotsinglevar.py --log -o test.png plt00000/ tfromp
\end{verbatim}
This will make a plot of ``tfromp'' from the plotfile {\tt plt00000} with log scaling,
and store the output in {\tt test.png}.  See Figure~\ref{fig:python}.
If you don't do `{\tt -o}', then a default output filename consisting of the
plotfile name + component will be used.

\begin{figure}[t]
\centering
\includegraphics[height=0.4\textheight]{\visfigpath/plt00000_tfromp}
\caption{\label{fig:python} Plot of {\tt test2} done with the python
  script {\tt plotsinglevar.py}.}
\end{figure}

If you list 2 different variables after the plotfile name, then they
will be plotted side-by-side in a single figure.  For example, 
\begin{verbatim}
plotsinglevar.py plt00000/ tfromp enucdot
\end{verbatim}
produces the output shown in figure~\ref{fig:python_two}.

\begin{figure}[t]
\centering
\includegraphics[height=0.4\textheight]{\visfigpath/plt00000_tfromp_enucdot}
\caption{\label{fig:python_two} Plot of {\tt test2} done with the
  python script {\tt plotsinglevar.py} showing 2 variables plotted
  from a single plotfile.}
\end{figure}

Additional options include `{\tt -m}' to specify the minimum data
value, `{\tt -M}' to specify the maximum data value, and `{\tt --eps}'
to make an EPS plot instead of PNG.  Running the script with no parameters
will give the full list available options.

Limited 3-d support is available.  When run as with a plotfile name
and variable, it will plot slices ($x$-$y$, $x$-$z$, and $y$-$z$) 
through the center of the domain.  The option `{\tt --origin}'
will put the slices through the origin.

%-----------------------------------------------------------------------------
% yt
%-----------------------------------------------------------------------------
\section{Visualizing with \yt}
\yt is a Python package for analyzing and visualizing simulation data.
Originally \yt was written for the {\tt Enzo} code, with focus on
cosmological simulation data.  It has since been refactored to remove
the specific {\tt Enzo}isms, and now can work on various data formats,
such as the BoxLib data from \maestro\ and \castro, HDF5 data
from {\tt FLASH}, and data from the SPH code {\tt Gadget}.  For more
information, see the \yt homepage at {\tt http://yt.enzotools.org/}.
